%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Raghav Kataria} \\ \vspace{1pt}
    \small +91 9253023990 $|$ \href{mailto:raghavkatariaaa@gmail.com}{\underline{raghavkatariaaa@gmail.com}} $|$ 
    \href{https://linkedin.com/in/raghav--kataria}{\underline{linkedin.com/in/raghav--kataria}} $|$
    \href{https://github.com/binaryboom}{\underline{github.com/binaryboom}}
\end{center}



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Java, Python, C++} \\
     \textbf{Web Development}{:  React.js, Next.js, Node.js, Nest.js, Express.js, TypeScript, JavaScript, Tailwind, HTML5, CSS3} \\
     \textbf{Tools \& Deployment}{: Git, GitHub, Burpsuite, Docker, Prisma, Jira, Render, Vercel} \\
     \textbf{Databases}{: MongoDB, SQL, PostgreSQL} \\
     \textbf{Problem Solving}{: Solved 300+ LeetCode problems in Java, covering various Algorithms and Data Structures} \\
     \textbf{Others}{: Cybersecurity (Bug Hunting) , RESTful API Development, Authentication, Web Sockets} 
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{SensAI}}{\underline{\href{https://sensai-interview.vercel.app}{sensai-interview.vercel.app}}}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application that simulates technical and behavioral interviews using AI, helping users prepare for real job interviews.}
            \resumeItem{Implemented multiple interview modes (Resume Insight, Code Mastery, Hands-On Q\&A, Culture Fit) to provide personalized interview experiences.}
            \resumeItem{Integrated speech recognition and synthesis for interactive, voice and video based Q\&A, where the AI interviewer analyzes responses,
 cross-questions candidates, and helps them practice confidently.}
          \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Pictogram}}{\underline{\href{https://pictogram-wqnp.onrender.com}{pictogram-wqnp.onrender.com}}}
          \resumeItemListStart
            \resumeItem{Built a full-stack social media platform, featuring secure authentication, image uploads, and core interactions (likes, comments, follow/unfollow).}
            \resumeItem{Integrated AI-powered comment moderation to automatically detect and filter harmful or inappropriate content.}
            \resumeItem{Developed real-time messaging and notification system using WebSockets to enable instant communication between users.}
          \resumeItemListEnd
          \resumeProjectHeading
        {\textbf{Boom}}{\underline{\href{https://boom-videochat.vercel.app}{boom-videochat.vercel.app}}}
          \resumeItemListStart
            \resumeItem{Developed a video chat application using Next.js and TypeScript with secure authentication powered by Clerk.}
            \resumeItem{Integrated GetStream Video API to enable video conferencing with screen sharing, live reactions, recording, scheduling, and meeting history.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer I}{July 2025 -- Present}
      {Nighthack Labs}{}
      \resumeItemListStart
        \resumeItem{Developing a real estate valuation platform for banks with AI features like interactive chat with property documents,speech-to-text and OCR-based document parsing, reducing manual data entry by 90\%.}
        \resumeItem{Implemented scalable backend services with Nest.js, Prisma, PostgreSQL, Docker and frontend modules in React, with secure authentication, authorization, and rate limiting.}
        \resumeItem{Built dashboards to display revenue metrics, employee performance, and report turnaround times, projected to improve workflow efficiency by 50\%.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Full Stack Developer Intern}{June 2024 -- Aug. 2024}
      {Belrise Industries}{\underline{\href{https://drive.google.com/file/d/1k_RoJDjhhmsAWKPBp4W3fEAqh_EDfGZZ/view}{Certificate}}}
      \resumeItemListStart
        \resumeItem{Developed an internal inventory management system using MongoDB, Express.js, React.js, and Node.js, reducing manual stock tracking time by 70\%.}
        \resumeItem{Implemented secure JWT authentication and role-based access, managing a database of over 2,000 items.}
        \resumeItem{Automated reporting and notifications for 5 departments, improving workflow efficiency and providing near real-time inventory insights.}
      \resumeItemListEnd


      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

   

    

  \resumeSubHeadingListEnd


  %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Applications}{CGPA: 8.9/10}
      {Maharaja Surajmal Institute, New Delhi}{Oct. 2022 -- June 2025}
    \resumeSubheading
      {Higher Secondary Education (Class XII)}{Percentage: 83\%}
      {DAV Police Public School, Panipat}{Apr. 2021 -- Mar 2022}
    \resumeSubheading
      {Secondary Education (Class X)}{Percentage: 91\%}
      {DAV Police Public School, Panipat}{Apr. 2019 -- Mar 2020}
  \resumeSubHeadingListEnd






%



%-------------------------------------------
\end{document}
